\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{IME} % Sets Journal name


\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Explainable Machine Learning Approaches for Modeling Shock Lapse in Term Life Contracts},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header



\begin{document}
\begin{frontmatter}

  \title{Explainable Machine Learning Approaches for Modeling Shock Lapse in Term
Life Contracts}
    \author[rstudio]{Kevin Kuo\corref{c1}}
   \ead{kevin.kuo@rstudio.com} 
   \cortext[c1]{Corresponding Author}
    \author[kpmg]{Frankie Logan}
   \ead{flogan@kpmg.com} 
  
    \author[arcga]{Bob Crompton}
   \ead{bob.crompton@arcga.com} 
  
      \address[rstudio]{RStudio}
    \address[kpmg]{KPMG}
    \address[arcga]{Actuarial Resources Corporation of Georgia}
  
  \begin{abstract}
  This is the abstract.
  
  It consists of two paragraphs.
  \end{abstract}
  
 \end{frontmatter}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{data}{%
\section{Data}\label{data}}

Discuss data from Rozar, Rushing, and Willeat (2010)

\hypertarget{modeling-approaches}{%
\section{Modeling approaches}\label{modeling-approaches}}

\hypertarget{soa-2015-report}{%
\subsection{SOA 2015 Report}\label{soa-2015-report}}

Discuss model from Xu et al. (2015).

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{evaluation}{%
\subsection{Evaluation}\label{evaluation}}

Discuss evaluation metric and tarin/test split.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{model-explanation}{%
\subsection{Model explanation}\label{model-explanation}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-soa2010}{}%
Rozar, Tim, Scott Rushing, and Susan Willeat. 2010. ``Report on the
Lapse and Mortality Experience of Post-Level Premium Period Term
Plans.'' Society of Actuaries.

\leavevmode\hypertarget{ref-soa2015}{}%
Xu, Richard, Dihui Lai, Minyu Cao, Scott Rushing, and Tim Rozar. 2015.
``Lapse Modeling for the Post-Level Period.'' Society of Actuaries.

\end{document}


